---
title: "Homework"
author: "Xuqian Tan"
date: "1/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Original Code
```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

##My function & Documentation:
####Function name: Analysis
####Description: This function takes in a stirng of protein name, analyzes protein drug interactions by reading in any protein PDB data and outputs a plot for the specified protein
####Input: name -> a string of the name of the interested protein
####Output: a plot of protein drug interaction of the interested protein
```{r}
Analysis <- function(name) {
  s <- read.pdb(name)
  s.chainA <- trim.pdb(s, chain="A", elety="CA")
  s.b <- s.chainA$atom$b
  plotb3(s.b, sse=s.chainA, typ="l", ylab="Bfactor")
}
```

###test
```{r}
names <- c("4AKE", "1AKE", "1E4Y")
for (i in names){
  Analysis(i)
}
```
