---
title: "Class06"
author: "Xuqian Tan"
date: "1/24/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Section 1: Reading files again :-)

Here we are going to try using the **read.table()** function and friends to read some example flat files 

First lets try adding a simple plot
```{r}
plot(1:10)

```

Back to file reading...
```{r}
read.table("https://bioboot.github.io/bimm143_W19/class-material/test1.txt", header = TRUE, sep = ",")
```

For this common CSV, we could use **read.csv()**
```{r}
file1 <- "https://bioboot.github.io/bimm143_W19/class-material/test1.txt"
read.csv(file1)
```

Read other files
```{r}
table2 <- read.table("https://bioboot.github.io/bimm143_W19/class-material/test2.txt", header = TRUE, sep = "$")
table3 <- read.table("https://bioboot.github.io/bimm143_W19/class-material/test3.txt", header = FALSE)
table2
table3
```

## Section 2, R functions

My first silly function
```{r}
add <- function(x, y=1) {
  # Sum the input x and y
  x + y
}
```

Let's try using the function
```{r}
add(1)
add(1,100)
add(c(1,2,3),4)
```

```{r}
rescale <- function(x) {
  rng <-range(x)
  (x - rng[1]) / (rng[2] - rng[1])
}
```

test on a small example where we know what the answer should be
```{r}
rescale(1:10)
```
```{r}
rescale(c(1,2,NA,3,10))
```

```{r}
rescale2 <- function(x) {
  rng <-range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}

rescale2(c(1,2,NA,3,10))
```

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
  rng <-range(x, na.rm=na.rm)
  print("Hello")
  answer <- (x - rng[1]) / (rng[2] - rng[1])
  print("is it me you are looking for?")
  if(plot) {
    plot(answer, typ="b", lwd=4)
  }
  print("I can see it in ...")
  return(answer)
}
```

```{r}
rescale3(c(1:6, NA, 10), plot = TRUE)
```


## Hands on section 1B
```{r}
# Can you improve this analysis code?
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

```{r}
Analysis <- function(name) {
  s <- read.pdb(name)
  s.chainA <- trim.pdb(s1, chain="A", elety="CA")
  s.b <- s1.chainA$atom$b
  plotb3(s.b, sse=s.chainA, typ="l", ylab="Bfactor")
}
```

test
```{r}
names <- c("4AKE", "1AKE", "1E4Y")
for (i in names){
  Analysis(i)
}
```





