---
title: "Class 14:Genome Informatics I"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Asthma SNPs in MXL population

Read file from Ensemble
http://uswest.ensembl.org/Homo_sapiens/Variation/Sample?db=core;r=17:39894595-39895595;v=rs8067378;vdb=variation;vf=362656008#373531_tablePanel

```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")
head(mxl)
```


How many of each genotypes are in this set
```{r}
table(mxl$Genotype..forward.strand.)
```

How many G|G genotype are in this set
```{r}
sum(mxl$Genotype..forward.strand. == "G|G")
```

percent values
```{r}
table(mxl$Genotype..forward.strand.)/nrow(mxl)*100
```

## RNA-Seq
Fastq quality score

Q. dose the first sequence have good quality
```{r}
#install.packages("seqinr")
#install.packages("gtools")
```

```{r}
q <- "DDDDCDEDCDDDDBBDDDCC@"
library(seqinr)
library(gtools)

asc(s2c(q)) -33
```


## Population sacle analysis 
Does the genotype for rs9067378 influence expression of the important asthema linked genes we found
```{r}
geno <- read.table("rs8067378_ENSG00000172057.6.txt")
head(geno)
```

```{r}
table(geno$geno)
```

```{r}
inds <- geno$geno == "G/G"
summary(geno$exp[inds])
```

```{r}
inds.aa <- geno$geno == "A/A"
summary(geno$exp[inds.aa])
```

```{r}
inds.ag <- geno$geno == "A/G"
summary(geno$exp[inds.ag])
```

Some nice figure that shows the distribution of these expression values?
box plot
```{r}
boxplot(exp~geno, geno)
```



