---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Section1. The PDB
Q1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” > “by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and determine the percentage of structures solved by X-Ray and Electron Microscopy. From the website what proportion of structures are protein? Aim to have a rendered GitHub document with working code that yields your answers.

```{r}
stats <- read.csv("Data Export Summary.csv")
```

```{r}
percent <- stats$Total/sum(stats$Total)*100
names(percent) <- stats$Experimental.Method
percent
```

Q2: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?


##Section3 Introduction to Bio3D in R
```{r}
library(bio3d)
example(plot.bio3d)
```

```{r}
pdb <- read.pdb("1hsg")
pdb
```

Q6. How many amino acid residues are there in this pdb object and what are the two nonprotein residues?
```{r}
attributes(pdb)
```
```{r}
#access the atom attribute or component use pdb$atom:
head(pdb$atom)
```

```{r}
# Print a subset of $atom data for the first two atoms
pdb$atom[1:2, c("eleno", "elety", "x","y","z")]
# Note that individual $atom records can also be accessed like this
pdb$atom$elety[1:2]
# Which allows us to do the following
plot.bio3d(pdb$atom$b[pdb$calpha], sse=pdb, typ="l", ylab="B-factor")
```


```{r}
# Select all C-alpha atoms (return their indices)
ca.inds <- atom.select(pdb, "calpha")
ca.inds
# Print details of the first few selected atoms
head( pdb$atom[ca.inds$atom, ] )
```

Q8. Use the Bio3D write.pdb() function to write out a protein only PDB file for viewing in VMD. Also write out a second separate PDB file for the ligand with residue name MK1

We want to select out the protein and drug only parts of these meolecular PDB files
```{r}
prot.inds <- atom.select(pdb, "protein")
prot.inds
prot.pdb <- trim.pdb(pdb, prot.inds)
write.pdb(prot.pdb, file = "protein.pdb")
```

let's do the same thing for our drug
```{r}
lig.inds <- atom.select(pdb, "ligand")
lig.pdb <- trim.pdb(pdb, lig.inds)
write.pdb(lig.pdb, file = "ligand.pdb")
```




