---
title: "Class13"
author: "Xuqian Tan"
date: "2/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Prepare HIV-protase molecule for docking

first get a PDB structure from the online database then clean it up for docking
```{r}
library(bio3d)
file.name <- get.pdb("1hsg")
```

Read file into R and clean it up (remove non-protein bits) and also we will save the ligand into a seperate file.
```{r}
hiv <- read.pdb(file.name)
hiv
#remove the non-protein part so that Non-protein/nucleic count is 0
prot <- trim.pdb(hiv, "protein")
prot
lig <- trim.pdb(hiv, "ligand")
lig
```

```{r}
write.pdb(prot, file="1hsg_protein.pdb")
```

```{r}
write.pdb(lig, file="1hsg_ligand.pdb")
```


Q1: What is the name of the two non protein resid values in this structure? What does resid correspond to and how would you get a listing of all reside values in this structure?
```{r}
#A1: HOH (127), MK1 (1)
```


```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```


## Normal Mode Analysis
```{r}
pdb <- read.pdb("1HEL")
m <- nma(pdb)
plot(m)
```


```{r}
mktrj(m, mode = 7, file = "nma_7.pdb")
```






