---
title: "Mini_Project"
author: "Xuqian Tan"
date: "2/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Preparing Data
read data set
```{r}
fna.data <- "WisconsinCancer.csv"
wisc.df <- read.csv(fna.data)
```

see the first 6 rows of data
```{r}
head(wisc.df)

#How many samples (i.e patients) are there in this data set
nrow(wisc.df)
```

Convert the features of the data: wisc.data
```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```

add row names to our new matrix of data
```{r}
# Set the row names of wisc.data
row.names(wisc.data) <- wisc.df$id
head(wisc.data)
```

Setup a separate new vector called diagnosis to be 1 if a diagnosis is malignant ("M") and 0 otherwise. Note that R coerces TRUE to 1 and FALSE to 0
```{r}
# Create diagnosis vector by completing the missing code
diagnosis <- as.numeric(wisc.df$diagnosis == "M")
```


##Exploratory data analysis
Q1. How many observations are in this dataset?
```{r}
nrow(wisc.data)
```

Q2. How many variables/features in the data are suffixed with _mean?
```{r}
inds <- grep("_mean", colnames(wisc.data))
length(inds)
```

Q3. How many of the observations have a malignant diagnosis?
```{r}
sum(diagnosis)
```


##Performing PCA

```{r}
# Check column means and standard deviations
colMeans(wisc.data)

apply(wisc.data,2,sd)
```

```{r}
# Perform PCA on wisc.data by completing the following code
wisc.pr <- prcomp(wisc.data, scale. = TRUE)
summary(wisc.pr)
```

Q4. From your results, what proportion of the original variance is captured by the first principal components (PC1)?
```{r}
Q4 = 44.27
```

Q5. How many principal components (PCs) are required to describe at least 70% of the original variance in the data?
```{r}
Q5 = 5
```

Q6. How many principal components (PCs) are required to describe at least 90% of the original variance in the data?
```{r}
Q6 = 10
```

```{r}
biplot(wisc.pr)
```

Generate a more standard scatter plot of each observation along principal components 1 and 2 (i.e. a plot of PC1 vs PC2 available as the first two columns of wisc.pr$x) and color the points by the diagnosis 
```{r}
plot(wisc.pr$x[,1] , wisc.pr$x[,2], col = diagnosis+1, xlab = "PC1", ylab = "PC2")
```

Variance captured by each PC
This info is in the $sdev component of our PCA result
```{r}
varance <- wisc.pr$sdev^2
pve <- round(varance/sum(varance)*100,1)
```

```{r}
plot(pve, type = "o")
```

Alternative scree plot of the same data, note data driven y-axis
```{r}
barplot(pve, ylab = "Precent of Variance Explained", names.arg=paste0("PC",1:length(pve)), las=2, axes = FALSE)
axis(2, at=pve, labels=round(pve,2))
```


##Hierarchical clustering

```{r}
# Scale the wisc.data data: data.scaled
data.scaled <- scale(wisc.data)
#Calculate the (Euclidean) distances between all pairs of observations
data.dist <- dist(data.scaled)
#Create a hierarchical clustering model using complete linkage. Manually specify the method argument to hclust() 
wisc.hclust <- hclust(data.dist, method = "complete")
```

```{r}
plot(wisc.hclust)
abline(h = 19, col="red", lty=2)
```

Use cutree() to cut the tree so that it has 4 clusters
```{r}
wisc.hclust.clusters <- cutree(wisc.hclust, k = 4)
#Use the table() function to compare the cluster membership to the actual diagnoses
table(wisc.hclust.clusters, diagnosis)
```


##Clustering on PCA space
For clustering we need:
1. Distance matrix
2. Clustering function
3. Cutree

This was the PCA result of PC1 and PC2
```{r}
plot(wisc.pr$x[,1] , wisc.pr$x[,2], col = diagnosis+1, xlab = "PC1", ylab = "PC2")
```

```{r}
pc.dist <- dist(wisc.pr$x[,1:2])
pc.hclust <- hclust(pc.dist, method = "ward.D2")
plot(pc.hclust)
```


```{r}
grps2 <- cutree(pc.hclust, k=2)
table(grps2)
```

```{r}
table(grps2, diagnosis)
```

```{r}
plot(wisc.pr$x[,1:2], col=grps2)
plot(wisc.pr$x[,1:2], col=diagnosis+1)
```

##Prediction

```{r}
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
npc
```

```{r}
plot(wisc.pr$x[,1:2], col=grps)
points(npc[,1], npc[,2], col="blue", pch=16)
```



